Dataset of operator-client dialogues aligned with knowledge-base queries

### 2016-06-24 paper.tex
x
citations

\title{Collecting operator-client conversation aligned with knowledge-base queries}
%If Title is too long, use \titlerunning
%\titlerunning{Short Title}

@@

Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data\cite{alex},\cite{todo}, but require non-trivial amount of expert work, or are gradually improved from initial policy through live user interaction\cite{Pomdp-young,gasix}, and lately are trained using supervised learning typically in end-to-end manner\cite{Wen2016,Williams2016}.\footnote{The~work of \cite{Williams2016} also fine tuned the conversation with reinforcement learning after the supervised-learning stage.}
The reinforce learning on one hand need just collect enough live user conversation without any transcription with the exception of explicit feedback at the end of each dialogue, but because the feedback signal is typically rather noise and delayed one require thousands of live conversations to improve rather simple policy.\cite{gasic}
The supervised-learning methods greatly reduced the number of conversation needed for training reasonable policy to few hundreds\cite{Wen2016}, but require annotation for all components used the dialogue which so far included at least a dialogue state\cite{Wen, his}.
Since the dialogue state is simplification of dialogue history and has no broadly-accepted form, it is very expensive to collect such annotated data because the dialogue state typically differs among domains and its structure is hard to explain to annotators.
In this paper, we focus on collecting supervised training set with rich enough annotation so the supervised models similar to~\cite{Wen2016} can be trained with few hundreds of dialogues, but the annotation of dialogues are much easier to collect.

We believe that the present dataset can be used for first experiments for end-to-end systems using supervised learning without annotated dialogue state.
The resulting systems should be able to roughly compare to systems trained on datasets with \cite{dstsc2, dstc3} dialogue state annotation because the same settings, i.e.\ database and task, for data collection.
Despite the fact, we collected human-to-human dialogues on known task of Cambridge restaurant domains the data-collecting method is completely domain and language independent.

@@

It was shown that few hundreds of annotated domain specific conversation is needed for training relatively well performing LU~\cite{Alex} as well as Dialogue State Tracking~\cite{todo-Young?} components.
The work of~\cite{dusek} and~\cite{Marraise} showed that also several hundreds of conversations with appropriate annotation is needed for training usable NLG unit on simple domains.
Even the crucial task of action selection with reward provided only at the end of dialogue can be trained using POMDP dialogue manager and few thousands conversations~\cite{Gasic}.

A~novel work of~\cite{Wen} showed that only XY conversation annotated with just at dialogue state level is needed for training the whole end-to-end system performing the task of summarizing the dialogue history and reply planning and generation.
Consequently, we believe that end-to-end systems even with latent variables can be trained using few hundreds conversation if additional supervision in the form of simple annotation is used for narrow goal-oriented domains such as~\cite{Wen} domain or Cambridge restaurant domain~\cite{DSTC2}.

We note that on one hand further annotation of dialogue conversation may help to train the models faster, but simply collecting more data is typically more beneficial even with less annotation for models which does not require such annotation.
As a consequence, we see work of~\cite{Wen},~\cite{Borders} and~\cite{Williams} as great step forward since there work use annotation on dialogue state level or even no annotation for training dialogue agents.

@@

Our data collection processed aimed at collecting natural conversation in the well defined domain.
We selected well studied Cambridge restaurant domain since the previous dataset~\cite{dstc1, dstc2, dstc3} in that domain demonstrated that a meaningful and not too long conversation can be held in the domain.
Also it was proven that the domain is on one hand difficult enough that even the state-of-the art systems does not reach human-level performance in the role of the operator and on the other hand numerous systems~\cite{young, gasic, Wen} demonstrated that are able to provide information to the clients most of the time.

We defined our domain by choosing a database from Dialogue State Tracking Challenge 2 (DSTC2)~\cite{dstc2} and explaining the interlocutors that there two roles a client and a operator.
For each conversation we determined goals for the client and provided the database for the operator.
We used the CrowdFlower (CF) crowdsourcing platform to collect the conversations.

@@

Our work is closely related  to work of~\cite{dstc1, dstc2, dstc3} in the sense that the conversation are held in the same domain.
On the other hand, the collection process differs substantially because we do not use any artificial system and rather we focus on collecting high quality human conversations. In addition, in our work we do not collect complicated annotation on LU and DST level as it was previously done on DST challenges.

A very relevant work of~\cite{Wen} collected human-human dialogues in similar domain to the Cambridge domain according their description.
Their dataset is not yet published so we compare only with their statistics.
The dataset is of similar size and used very similar collection scheme where the Amazon Mechanical Turk workers submitted one reply at a time without being connected to each other in real-time.

Another line of research~\cite{mirek-interactive} used CF to collect human-human conversation for interactive-learning dataset.
However, the collected dialogues were later annotated by expert annotators which goes directly against our intentions to avoid any expensive annotations.

There is tremendous amount of work describing Wizard of Oz experiments~\cite{walker,schlangen,someone} which either focused on studying linguistic properties of dialogues, evaluated proof of concept or even collected bootstrap training data, but definitely, according our knowledge, do not use cheap crowdsourcing workers to collect a~full training dataset.

\section{Conclusion and Future work}
\label{sec:conc}
We present a new human-human dialogue dataset with annotation of user intension in form of their database calls.
We also introduced a novel data collection setting which resembles work of operators in call centers and introduce minimum overhead to crowdsourcing workers.

The collected dialogues are published under Creative Commons 4.0 BY-SA license on available to download at {\it anonymised}.  % lindat\footnote{todo where}.

>>>>

\title{Dataset of operator-client dialogues aligned with knowledge-base queries}
%If Title is too long, use \titlerunning
%\titlerunning{Short Title}

@@

Current Spoken Dialogue Systems (SDS) are either handcrafted and use no training data\cite{duvsek2014alex},\cite{raux2005let}, but require non-trivial amount of expert work, or are gradually improved from initial policy through live user interaction\cite{young2010hidden,gasic2011line}, and lately are trained using supervised learning typically in end-to-end manner\cite{wen2016network,williams2016end}.\footnote{The~work of \cite{williams2016end} also fine tuned the conversation with reinforcement learning after the supervised-learning stage.}
The reinforce learning on one hand need just collect enough live user conversation without any transcription with the exception of explicit feedback at the end of each dialogue, but because the feedback signal is typically rather noise and delayed one require thousands of live conversations to improve rather simple policy.\cite{gasic2011line}
The supervised-learning methods greatly reduced the number of conversation needed for training reasonable policy to few hundreds\cite{wen2016network}, but require annotation for all components used the dialogue which so far included at least a dialogue state\cite{wen2016network, young2010hidden}.
Since the dialogue state is simplification of dialogue history and has no broadly-accepted form, it is very expensive to collect such annotated data because the dialogue state typically differs among domains and its structure is hard to explain to annotators.
In this paper, we focus on collecting supervised training set with rich enough annotation so the supervised models similar to~\cite{wen2016network} can be trained with few hundreds of dialogues, but the annotation of dialogues are much easier to collect.

We believe that the present dataset can be used for first experiments for end-to-end systems using supervised learning without annotated dialogue state.
The resulting systems should be able to roughly compare to systems trained on datasets with \cite{williams2013dstc1, henderson2014dstc2, henderson2014dstc3} dialogue state annotation because the same settings, i.e.\ database and task, for data collection.
Despite the fact, we collected human-to-human dialogues on known task of Cambridge restaurant domains the data-collecting method is completely domain and language independent.

@@

It was shown that few hundreds of annotated domain specific conversation is needed for training relatively well performing LU~\cite{duvsek2014alex} as well as Dialogue State Tracking~\cite{young2010hidden} components.
The work of~\cite{duvsek2014alex} and~\cite{mairesse2010phrase} showed that also several hundreds of conversations with appropriate annotation is needed for training usable NLG unit on simple domains.
Even the crucial task of action selection with reward provided only at the end of dialogue can be trained using POMDP dialogue manager and few thousands conversations~\cite{gasic2011line}.

A~novel work of~\cite{wen2016network} showed that only XY conversation annotated with just at dialogue state level is needed for training the whole end-to-end system performing the task of summarizing the dialogue history and reply planning and generation.
Consequently, we believe that end-to-end systems even with latent variables can be trained using few hundreds conversation if additional supervision in the form of simple annotation is used for narrow goal-oriented domains such as~\cite{wen2016network} domain or Cambridge restaurant domain~\cite{henderson2014dstc2}.

We note that on one hand further annotation of dialogue conversation may help to train the models faster, but simply collecting more data is typically more beneficial even with less annotation for models which does not require such annotation.
As a consequence, we see work of~\cite{wen2016network},~\cite{bordes2016learning} and~\cite{williams2016end} as great step forward since there work use annotation on dialogue state level or even no annotation for training dialogue agents.

@@

Our data collection processed aimed at collecting natural conversation in the well defined domain.
We selected well studied Cambridge restaurant domain since the previous dataset~\cite{williams2013dstc1, henderson2014dstc2, henderson2014dstc3} in that domain demonstrated that a meaningful and not too long conversation can be held in the domain.
Also it was proven that the domain is on one hand difficult enough that even the state-of-the art systems does not reach human-level performance in the role of the operator and on the other hand numerous systems~\cite{young2010hidden, gasic2011line, wen2016network} demonstrated that are able to provide information to the clients reasonable well.

We defined our domain by choosing a database from Dialogue State Tracking Challenge 2 (DSTC2)~\cite{henderson2014dstc2} and explaining the interlocutors that there two roles a client and a operator.
For each conversation we determined goals for the client and provided the database for the operator.
We used the CrowdFlower (CF) crowdsourcing platform to collect the conversations.

@@

Our work is closely related  to work of~\cite{williams2013dstc1, henderson2014dstc2, henderson2014dstc3} in the sense that the conversation are held in the same domain.
On the other hand, the collection process differs substantially because we do not use any artificial system and rather we focus on collecting high quality human conversations. In addition, in our work we do not collect complicated annotation on LU and DST level as it was previously done on DST challenges.

A very relevant work of~\cite{wen2016network} collected human-human dialogues in similar domain to the Cambridge domain according their description.
Their dataset is not yet published so we compare only with their statistics.
The dataset is of similar size and used very similar collection scheme where the Amazon Mechanical Turk workers submitted one reply at a time without being connected to each other in real-time.

Another line of research~\cite{vodolan2016data} used CF to collect human-human conversation for interactive-learning dataset.
However, the collected dialogues were later annotated by expert annotators which goes directly against our intentions to avoid any expensive annotations.

There is significant amount of work which used Wizard of Oz experiments~\cite{whittaker2002fish,walker1997evaluating,rieser2008learning} for studying linguistic properties of dialogues, evaluating proof of concept or even collecting bootstrap training data, but according our knowledge no other work than~\cite{We} have not used cheap crowdsourcing workers to collect a~full training dataset for supervised learning.

\section{Conclusion and Future work}
\label{sec:conc}
We present a new human-human dialogue dataset with annotation of user intension in form of their database calls.
We also introduced a novel data collection setting which resembles work of operators in call centers and introduce minimum overhead to crowdsourcing workers.
The collected dialogues are published under Creative Commons 4.0 BY-SA license on available to download at {\it anonymised}.  % lindat\footnote{todo where}.

We plan to increase the number of collected dialogues till the camera ready deadline to XYZU.
We intend to use the dataset to train and evaluate an~end-to-end conversational model which uses only the database calls as additional supervision to the recorded responses.
